### 2016-06-01 paper/fig_regex-syntax.tex
Bunch of small comments
fixed benjmain's suggestions, half of appendix

\begin{figure}
\centering
\begin{tabular}{l@{\ }l@{\ }c@{\ }l@{\ }r}

% REGEX
(Regexs)& \Regex{} & \GEq{} & \RegexVariable{} & variable \\
& & & \GBar{} s $\in \Sigma^*$ & base \\
& & & \GBar{} \Regex{}* & star \\
& & & \GBar{} $\Regex_1 \Regex_2$ & concat \\
& & & \GBar{} $\Regex_1 | \Regex_2$ & or \\
\end{tabular}
\caption{Regex Syntax}
\label{fig:regex-syntax}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tabular}{l@{\hspace*{5mm}}l@{\ }c@{\ }l@{\hspace*{5mm}}l}

% REGEX
(String)& \String{},\StringAlt{} & \GEq{} & $\String\in\Star{\Sigma}$ \\
(Regexs)& \Regex{},\RegexAlt{} & \GEq{} & s & \it Base \\
& & & \GBar{} \Regex{}* & \it Star \\
& & & \GBar{} $\RegexConcat{\Regex_1}{\Regex_2}$ & \it Concat \\
& & & \GBar{} $\Regex_1 | \Regex_2$ & \it Or \\
\end{tabular}
\caption{Regex Syntax \bcp{Recommend using capital letters ($R$, $S$,
    ...) for regular expressions.  And left-justifying the RH column and
    putting it in italic (with more space separating it from the rest) so
    that it's clear that it's commentary.}}
\label{fig:regex-syntax}
\end{figure}
